### 2019-05-22 ch0_frontmatter.tex
update document

	{\Huge \textsf{Proteomic analysis of \textit{Taenia} spp. excretion/secretion proteins: the search for \textit{Taenia solium}-specific diagnostic antigens}}

@@

	{\textsf{A thesis submitted in fulfillment of the requirements for the degree of \\Doctor in Computer Science, 2019}}

>>>>

	{\Huge \textsf{Studying dynamic processes\\with networks and trajectories}}

@@

	{\textsf{Thesis submitted in fulfilment of the requirements for the degree of \\Doctor in Computer Science, 2019}}
